intRo

### 2015-01-06 departmental-seminar/index.Rmd
first draft of slides

---
title: "`intRo`"
subtitle: "Statistical Analysis Software for Teaching"
author: "Andee Kaplan & Eric Hare"
date: "January 12, 2015"
output: ioslides_presentation
font-family: Helvetica
ioslides_presentation:
    logo: images/icon.png
    widescreen: true
---

@@

## What is `intRo`?
 - A modern **web-based** application for performing basic data analysis and statistical routines
 - Built using `R` and `Shiny`
 - Powerful and extensible modular structure
 - Simple enough for the novice statistician
 - Meant to assist in the learning of statistics rather than a stand-alone deliverer of statistics education

@@

**Ulterior motive**: get students excited about programming
 - By navigating about the user interface of `intRo`, students are creating a fully-executable `R` script that they can download and run locally
 - Viewing their script change real-time within the application

## Extensible
 - User interaction with `intRo` is split into bitesize chunks that we call *modules*
 - Each module is a self contained set of `R` code that is dynamically added to the application at run time
 - `intRo` can be easily extended by the addition of modules within the frame-work underlying the application
 - Allows `intRo` to be tailored to the needs of a particular course

@@

## Tradeoffs
There were a number of challenges we encountered in striving to strike the balance of functionality and ease-of-use:

@@

## Presenting choices (Cont'd)
<img src="images/graphical_table.png" height="275">

@@

## Module creation package
*Modularity* is a key feature of `intRo`, but module creation is currently:
 - Undocumented
 - Entirely manual
 - Unnecessarily lengthy

@@

## Server load
Limited testing has been done to assess how `intRo` handles heavy user load
 - Dozens of students at accessing app at once
 - Simultaneous larger computations like printing results

@@

## More classes
 - We would like to see `intRo` used in more classes
 - Module creation package will allow it to suit more curricula
 - We welcome collaborators interested in extending `intRo` to submit pull requests on GitHub (http://www.github.com/gammarama/intRo)
     - Additional modules
     - Improvements and bug fixes

>>>>

---
title: "intRo"
subtitle: "Statistical Analysis Software for Teaching"
author: "Andee Kaplan & Eric Hare"
date: "January 12, 2015"
output: ioslides_presentation
font-family: Helvetica
ioslides_presentation:
    logo: images/icon.png
    widescreen: true
---

@@

## What is `intRo`?
 - A modern **web-based** application for performing basic data analysis and statistical routines
 - Built using `R` and `Shiny`
 - Powerful and extensible modular structure
 - Simple enough for the novice statistician
 - Assists in the learning of statistics rather than acting as a stand-alone deliverer of statistics education

@@

**Ulterior motive**: get students excited about programming

 - By navigating about the user interface of `intRo`, students are creating a fully-executable `R` script that they can download and run locally
 - Viewing their script change real-time within the application

## Extensible
 - User interaction with `intRo` is split into bitesize chunks that we call *modules*
 - Each module is a self contained set of `R` code that is dynamically added to the application at run time
 - `intRo` can be easily extended by the addition of modules within the frame-work underlying the application
 - Allows instructors/collaborators to tailor `intRo` to the needs of a particular course

@@

## Tradeoffs
We encountered a number of challenges in striving to strike the balance of functionality and ease-of-use:

@@

## Presenting choices (Cont'd)
<img src="images/graphical_table.png">

@@

## Module creation package
*Modularity* is a key feature of `intRo`, but module creation is currently:

 - Undocumented
 - Entirely manual
 - Unnecessarily lengthy

@@

## Server load
Limited testing has been done to assess how `intRo` handles heavy user load

 - Dozens of students at accessing app at once
 - Simultaneous larger computations like printing results

@@

## More classes
 - We would like work with instructors to get `intRo` into more classes
 - Module creation package will allow it to suit more curricula
 - We welcome collaborators interested in extending `intRo` to submit pull requests on GitHub (http://www.github.com/gammarama/intRo)
     - Additional modules
     - Improvements and bug fixes
